### 2020-03-18 README.Rmd
Added TODO's based on meeting
working on fit_bayesian_model

#### Spatial cross-validation

@@

```{r}
focal_vs_comp_bw <- bw_growth_df %>% 
  create_focal_vs_comp(max_dist, model_specs = bw_specs, cv_grid = bw_cv_grid, id = "treeID")
```

@@

bw_predict %>%
  group_by(focal_ID) %>%
  summarise(growth = mean(growth), growth_hat = mean(growth_hat)) %>%
  ggplot(aes(growth, growth_hat)) +
  geom_point(size = 0.5, color = rgb(0,0,0,0.25)) +
  stat_smooth(method = 'lm') +
  geom_abline(slope = 1, intercept = 0) +
  labs(x = "Observed growth in dbh", y = "Predicted growth in dbh")
```

* `predict_bayesian_model()`. 
    + Inputs: `focal_and_comp`, `model_specs`, `posterior_param`
    + Output: `focal_and_comp` with updated `growth_hat` variable
* Show observed vs predicted growth
* CV: `run_cv()` is a wrapper to `fit_bayesian_model()` and `predict_bayesian_model()`. 
* Permutation test:
  + Add line to that shuffles competitor species within `focal_and_comp` just before fitting model
  + permutation AND CV: add `run_shuffle` argument to `run_cv()`

### Model output and performance

* Make plot posterior parameter functions

>>>>

#### Defining spatial cross-validation folds

@@

```{r}
focal_vs_comp_bw <- bw_growth_df %>% 
  create_focal_vs_comp(max_dist = max_dist, model_specs = bw_specs, cv_grid = bw_cv_grid, id = "treeID")
```

@@

# TODO: Convert output of predict_bayesian_model() to be of focal_vs_focal type
# TODO: Preserve geometry variable, that way we can easily create residual plots

bw_predict %>%
  group_by(focal_ID, focal_notion_of_species) %>%
  # Since for the same focal tree all growth & growth_hat values are the same:
  summarise(growth = mean(growth), growth_hat = mean(growth_hat)) %>%
  ggplot(aes(x = growth, y = growth_hat)) +
  geom_point(size = 0.5, color = rgb(0,0,0,0.25)) +
  stat_smooth(method = 'lm') +
  geom_abline(slope = 1, intercept = 0) +
  coord_fixed() + 
  labs(
    x = "Observed growth in dbh", y = "Predicted growth in dbh", 
    title = "Predicted vs Observed Growth"
  )
```

### Run spatial cross-validation

* CV: `run_cv()` is a wrapper to `fit_bayesian_model()` and `predict_bayesian_model()`.

### Run permutations

* Permutation test:
  + Add line to that shuffles competitor species within `focal_and_comp` just before fitting model
  + permutation AND CV: add `run_shuffle` argument to `run_cv()`

### Visualize posterior distributions

* Plot posterior distributions of all parameters
